\textbf{universal corpus}

### 2014-03-19 docs/computEL/liling.tex
updated tex on clustering results

According to ethnologue
Total Living languages: 7105
Total Living language families: 147

6,749
33,117

>>>>

\noindent
According to ethnologue \\
Total Living languages: 7105 \\
Total Living language families: 147 \\

\begin{table}[h!]
    \begin{tabular}{l|ccc|ccc}
    ~        & complete & ~       & ~       & ward    & ~       & ~       \\ \cline{2-7}
    ~        & precision & recall       & f-score       & precision    & recall       & f-score      \\ \hline
    distance & 0.0614   & 0.8565 & \textbf{0.1099} & 0.06140  & 0.8565 & \textbf{0.1099} \\
    maxclust & 0.1925  & \textbf{0.0927} & 0.0692 & \textbf{0.1963} & 0.0905 & 0.0686  \\
    \end{tabular}
\caption{Comparing of clustering algorithms where number of clusters is set to genetic grouping on Ethnologue.}
\end{table}

\noindent
see full table in http://goo.gl/bs2vPo
